RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-27 doc/paper.tex
Exp. section: working...

@@

>>>>

   \item From the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other approaches, as shown by the produced results w.r.t.\ different levels of noise in the input data. Moreover, this is a new state-of-the-art algorithms when one concerns the problem of SR.

@@

\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}

In this section we study scalability of our method in terms of different noise level in the input data as well as different complexity of the exact solutions (models).

First, we divide our benchmark sets into three parts as follows. 
\begin{itemize}
	\item Small--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 3 to 7 nodes belong to this sub-set.
	\item Middle--sized instances:  all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 8 to 11 nodes belong to this sub-set.
	\item Large--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 12 to 15 nodes belong to this sub-set. 
\end{itemize}

The results are displayed in Figure~\ref{fig:compExact_noise_size}. They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis). As expected, the success rate is the highest for the small--sized instances; it is sightly bellow 90\% for the clean (no-noise) data. For more noisy data, the success rate of the algorithm gets decreased. For example, on the small-sized instances on the noisy data with the level of noise of 0.01, the rate of success is about 35 \%.
